Test parsing of Proff.no table

### 2022-07-15 Test parsing of Proff table.Rmd
Adding Shiny links. Minor corrections.

## Function 6 visualisations
```{r}
ggplot(opera, aes(year, lederlonn)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "", big.mark = ".",
                                                   decimal.mark = ","))
opera |> 
  group_by(year) |> 
  transmute(
    sum = sum(lederlonn, leder_annen_godtgjorelse, na.rm = TRUE)
  ) |> 
  ggplot(aes(year, sum)) +
  geom_col()
opera
opera_lonn <- opera |> 
  group_by(year) |> 
  transmute(
    sum = sum(lederlonn, leder_annen_godtgjorelse, na.rm = TRUE) / arsresultat,
    profit = ifelse(arsresultat >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, sum, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_percent(scale = 1),
                     name = "Godtgjørelse") +
  xlab("År") +
  theme(legend.position = "none")

>>>>

## Function 6 visualisations
```{r}
ggplot(opera, aes(year, lederlonn)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "", big.mark = ".",
                                                   decimal.mark = ","))
opera |> 
  group_by(year) |> 
  transmute(
    sum = sum(lederlonn, leder_annen_godtgjorelse, na.rm = TRUE)
  ) |> 
  ggplot(aes(year, sum)) +
  geom_col()
opera
opera_lonn <- opera |> 
  group_by(year) |> 
  transmute(
    percentage = sum(lederlonn, leder_annen_godtgjorelse, na.rm = TRUE) / arsresultat,
    profit = ifelse(arsresultat >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, percentage, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_percent(scale = 1),
                     name = "Godtgjørelse") +
  xlab("År") +
  theme(legend.position = "none")
